---
title: "FiveThirtyEight"
output: html_document
---
Madison Nareski & Julie Reighard
```{r}
library(tidyverse)
library(fivethirtyeight)
head(drug_use)
```
```{r}
ggplot(data = drug_use, mapping = aes(x=alcohol_freq)) + geom_bar()+labs(x= "Alcohol Frequency",y="Number of Drinks", title="How Often People Drink" )


```
This graph represents the number of drinks a person has with how frequently the drink.
```{r}
ggplot(data = drug_use, mapping = aes(x=age, y=alcohol_use)) + geom_point()+labs(x="Age", y="Alcohol Use", title="Relationship Between Age and Alcohol Use")
```
This graph shows the relationship between how old someone is and how mant times they drink.
```{r}
ggplot(data = drug_use, mapping = aes(x=marijuana_use, y=alcohol_use,size=n, color=age)) + geom_point()+labs(x="Marijuana Use", y="Alcohol Use", title="Relationship Between Marijuana Use and Alcohol Use")
```
This graph shows the relationship between when people use alcohol and marijuana together along with their age, while the size represents how many people are doing both.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



